Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Blank out the home page and source code links.
Blind ICSI.

The ``domainless'' fronting style, which omits SNI,
is useful when there is no good front domain known for a web service.
At least one CDN, Fastly, requires the domainless style.
All current web browsers support SNI,
so it is possible that lack of SNI could be used as a distinguisher.
According to our communication with
a representative of the International Computer Science Institute's
certificate notary~\cite{icsi-notary},
which observes on the order of 50~million TLS connections daily,
83.5\% of connections used SNI in June~2014.
There are apparently enough connections without SNI
that a censor will at least have to consider seriously
the costs and benefits before deciding to block SNI-less TLS outright.

@@

\meek\ has a home page at
\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
Our source code is in the Git repository at
\url{https://git.torproject.org/pluggable-transports/meek.git}.
All our programs are free software.
% As of version 0.9 (June~19, 2014), the source code consists of
% about 1,100 lines of Go for the client programs,
% 400 lines for \meekserver, and
% 100 lines for the reflector application for App Engine.
% Each of the browser extensions
% (one for Firefox, one for Chrome)
% is about 400 lines of JavaScript.

>>>>

The ``domainless'' fronting style, which omits SNI,
is useful when there is no good front domain known for a web service.
At least one CDN, Fastly, requires the domainless style.
All current web browsers support SNI,
so it is possible that lack of SNI could be used as a distinguisher.
According to our communication with
a representative of
[a blinded organization observing many TLS connections],
% ANON
% the International Computer Science Institute's
% certificate notary~\cite{icsi-notary},
% which observes on the order of 50~million TLS connections daily,
83.5\% of connections used SNI in June~2014.
There are apparently enough connections without SNI
that a censor will at least have to consider seriously
the costs and benefits before deciding to block SNI-less TLS outright.

@@

% ANON
% \meek\ has a home page at
% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
% Our source code is in the Git repository at
% \url{https://git.torproject.org/pluggable-transports/meek.git}.
% All our programs are free software.

% As of version 0.9 (June~19, 2014), the source code consists of
% about 1,100 lines of Go for the client programs,
% 400 lines for \meekserver, and
% 100 lines for the reflector application for App Engine.
% Each of the browser extensions
% (one for Firefox, one for Chrome)
% is about 400 lines of JavaScript.
